Implications of Differential Evolution for Defect Prediction: Analytics Without Parameter Tuning Considered Harmful

### 2015-03-03 tuningpredictor.tex

After feature selection comes instance selection. There are many settings for instance selectors such as use outlier removal or prototype generation. Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
The next set of settings concern how many neighbors to use (k=1,2,5,etc). Some researchers set “k” in dynamic pre-learning phase that checks the training data to find what “k” works best for that data.

@@

\begin{figure*}
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\begin{minipage}{0.81\linewidth}
\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(precision) } \\
  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
\multicolumn{1}{c}{~}\\
antV0 & 30 &         & $\bigstar$ 89 & {\rfour} & 27 &         &$\bigstar$ 89 & {\rfour} & 40 & {\rone} &$\bigstar$ 89 & {\rfour}\\
antV1 & 32 &         &$\bigstar$ 74 & {\rfour} & 41 & {\rone} &$\bigstar$ 74 & {\rfour} & 57 & {\rtwo} &$\bigstar$ 74 & {\rfour}\\
antV2 & 78 & {\rfour} &$\bigstar$ 78 & {\rfour} & 52 &         & 67 & {\rthree} & 66 & {\rtwo} & 50 &        \\
camelV0 &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour} & 26 &         & 37 &         &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour}\\
camelV1 & 22 &         &$\bigstar$ 81 & {\rfour} & 23 &         & 25 &         & 28 &         & 28 &        \\
ivyV0 & 16 &         & 23 & {\rthree} & 18 & {\rone} &$\bigstar$ 25 & {\rfour} & 18 & {\rone} & 19 & {\rone}\\
jeditV0 & 35 &         & 75 & {\rthree} & 49 & {\rone} &$\bigstar$ 86 & {\rfour} & 52 & {\rone} & 50 & {\rone}\\
jeditV1 & 24 &         &$\bigstar$ 87 & {\rfour} & 28 &         & 62 & {\rthree} & 36 &         & 42 & {\rone}\\
jeditV2 & 2 &         &$\bigstar$ 98 & {\rfour} & 3 &         & 4 &         & 5 &         & 6 &        \\
log4jV0 & 94 &         &$\bigstar$100 & {\rfour} & 97 & {\rtwo} & 98 & {\rthree} &$\bigstar$ 100 & {\rfour} &$\bigstar$100 & {\rfour}\\
luceneV0 & 61 &         & 71 & {\rtwo} & 67 & {\rone} &$\bigstar$ 78 & {\rfour} & 69 & {\rtwo} & 70 & {\rtwo}\\
poiV0 & 70 &         &$\bigstar$ 92 & {\rfour} & 77 & {\rone} & 79 & {\rtwo} & 79 & {\rtwo} & 75 & {\rone}\\
poiV1 & 100 & {\rfour} &$\bigstar$ 89 & {\rfour} & 73 & {\rtwo} &$\bigstar$ 89 & {\rfour} & 86 & {\rthree} & 36 &        \\
synapseV0 & 66 & {\rthree} & 0 &         & 71 & {\rthree} &$\bigstar$ 95 & {\rfour} & 59 & {\rthree} & 67 & {\rthree}\\
velocityV0 & 34 &         & 34 &         & 34 &         &$\bigstar$ 45 & {\rfour} & 40 & {\rtwo} & 41 & {\rthree}\\
xercesV0 & 13 &         &$\bigstar$ 85 & {\rfour} & 14 &         & 73 & {\rfour} & 16 &         & 13 &        \\
xercesV1 &$\bigstar$ 56 & {\rfour} & 26 &         & 55 & {\rfour} & 26 &         & 41 & {\rtwo} & 26 &        \\
\end{tabular}
\end{minipage}\begin{minipage}{.15\linewidth}
\begin{tabular}{|p{\linewidth}|}\hline

precision percentile ranges:

Percentiles computed  separately
for each data set.\\\hline
\end{tabular}
\end{minipage}
\caption{Median precision values in tune once and test ten times experiment. 
Gray bars  show  precision values
discretized into 20th percentiles ranges from min to max.
All data available from http://openscience.us/repo/effort.
}\label{fig:nonc}
\end{figure*}

@@

\begin{figure*}
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\begin{minipage}{0.81\linewidth}
\begin{tabular}{r@{~}|r@{~}l@{~}|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|r@{~}l@{~}|r@{~}l@{~}|r@{~}l}
  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(F ) } \\
  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
\multicolumn{1}{c}{~}\\
antV0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
antV1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
antV2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
camelV0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
camelV1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
ivyV0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
jeditV0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
jeditV1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
jeditV2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
log4jV0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
luceneV0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
poiV0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
poiV1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
synapseV0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
velocityV0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
xercesV0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
xercesV1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
\end{tabular}
\end{minipage}\begin{minipage}{.15\linewidth}
\begin{tabular}{|p{\linewidth}|}\hline

@@

>>>>

After feature selection comes instance selection. There are many settings for instance selectors such as use outlier removal or prototype generation. Within each of those settings are number sub-choices such as the choice of outlier remover or prototype generator.
The next set of settings concern how many neighbors to use (k=1,2,5,etc). Some researchers set ``k'' in dynamic pre-learning phase that checks the training data to find what ``k'' works best for that data.

@@

\begin{figure}
\renewcommand{\baselinestretch}{0.8}

\scriptsize  
\begin{tabular}{r|r@{~}l@{~}|r@{~}l|r@{~}l|r@{~}l|r@{~}l@{~}|r@{~}l@{~}r@{~}l}
      &   \multicolumn{4}{c|}{WHERE}         &   \multicolumn{4}{c|}{CART}         &   \multicolumn{4}{c}{Random Forests}         \\\hline
  Data set   &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}         &   \multicolumn{2}{c}{Naive}         &   \multicolumn{2}{c|}{Tuned}    &   \multicolumn{2}{c}{Naive}  &   \multicolumn{2}{c}{Tuned}\\\hline

antV0 & 30 &         & $\bigstar$ 89 & {\rfour} & 27 &         &$\bigstar$ 89 & {\rfour} & 40 & {\rone} &$\bigstar$ 89 & {\rfour}\\
antV1 & 32 &         &$\bigstar$ 74 & {\rfour} & 41 & {\rone} &$\bigstar$ 74 & {\rfour} & 57 & {\rtwo} &$\bigstar$ 74 & {\rfour}\\
antV2 & 78 & {\rfour} &$\bigstar$ 78 & {\rfour} & 52 &         & 67 & {\rthree} & 66 & {\rtwo} & 50 &        \\
camelV0 &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour} & 26 &         & 37 &         &$\bigstar$ 83 & {\rfour} &$\bigstar$ 83 & {\rfour}\\
camelV1 & 22 &         &$\bigstar$ 81 & {\rfour} & 23 &         & 25 &         & 28 &         & 28 &        \\
ivyV0 & 16 &         & 23 & {\rthree} & 18 & {\rone} &$\bigstar$ 25 & {\rfour} & 18 & {\rone} & 19 & {\rone}\\
jeditV0 & 35 &         & 75 & {\rthree} & 49 & {\rone} &$\bigstar$ 86 & {\rfour} & 52 & {\rone} & 50 & {\rone}\\
jeditV1 & 24 &         &$\bigstar$ 87 & {\rfour} & 28 &         & 62 & {\rthree} & 36 &         & 42 & {\rone}\\
jeditV2 & 2 &         &$\bigstar$ 98 & {\rfour} & 3 &         & 4 &         & 5 &         & 6 &        \\
log4jV0 & 94 &         &$\bigstar$100 & {\rfour} & 97 & {\rtwo} & 98 & {\rthree} &$\bigstar$ 100 & {\rfour} &$\bigstar$100 & {\rfour}\\
luceneV0 & 61 &         & 71 & {\rtwo} & 67 & {\rone} &$\bigstar$ 78 & {\rfour} & 69 & {\rtwo} & 70 & {\rtwo}\\
poiV0 & 70 &         &$\bigstar$ 92 & {\rfour} & 77 & {\rone} & 79 & {\rtwo} & 79 & {\rtwo} & 75 & {\rone}\\
poiV1 & 100 & {\rfour} &$\bigstar$ 89 & {\rfour} & 73 & {\rtwo} &$\bigstar$ 89 & {\rfour} & 86 & {\rthree} & 36 &        \\
synapseV0 & 66 & {\rthree} & 0 &         & 71 & {\rthree} &$\bigstar$ 95 & {\rfour} & 59 & {\rthree} & 67 & {\rthree}\\
velocityV0 & 34 &         & 34 &         & 34 &         &$\bigstar$ 45 & {\rfour} & 40 & {\rtwo} & 41 & {\rthree}\\
xercesV0 & 13 &         &$\bigstar$ 85 & {\rfour} & 14 &         & 73 & {\rfour} & 16 &         & 13 &        \\
xercesV1 &$\bigstar$ 56 & {\rfour} & 26 &         & 55 & {\rfour} & 26 &         & 41 & {\rtwo} & 26 &        \\
\end{tabular}

\caption{Precision values in tune   and naive runs.
All data available from http://openscience.us/repo/effort. {\bf KEY:}
  percentile ranges:\newline
80th to 100th= {\rfour};
60th to 80th= {\rthree}; 
40th to 60th= {\rtwo};
20th to 40th= {\rone};
an absent bar shows  0th to 20th.
Percentiles computed  separately
for each row.

}\label{fig:nonc}
\end{figure}

@@

\begin{figure*}
\renewcommand{\baselinestretch}{0.8}
\scriptsize
\begin{minipage}{0.81\linewidth}
\begin{tabular}{r@{~}|r@{~}l|r@{~}l@{~}|r@{~}l|r@{~}@{~}l|@{~}r@{~}l|r@{~}l|@{~}r@{~}l}
  \multicolumn{1}{c|}{~}&\multicolumn{11}{c}{median(F ) } \\
  Data set   &   \multicolumn{2}{c}{Naive\_Where}         &   \multicolumn{2}{c}{Tuned\_Where}         &   \multicolumn{2}{c}{Naive\_CART}         &   \multicolumn{2}{c}{Tuned\_CART}    &   \multicolumn{2}{c}{Naive\_RanFst}  &   \multicolumn{2}{c}{Tuned\_RanFst}\\\hline
\multicolumn{1}{c}{~}\\
ant0 &$\bigstar$ 39 & {\rfour} & 26 & {\rone} & 32 & {\rtwo} & 25 &         & 25 &         & 22 &        \\
ant1 & 11 &         &$\bigstar$ 85 & {\rfour} & 40 & {\rone} & 49 & {\rtwo} & 39 & {\rone} & 33 & {\rone}\\
ant2 & 0 &         &$\bigstar$ 86 & {\rfour} & 44 & {\rtwo} & 51 & {\rtwo} & 52 & {\rthree} & 56 & {\rthree}\\
camel0 & 0 &         &$\bigstar$ 28 & {\rfour} & 9 & {\rone} &$\bigstar$ 28 & {\rfour} & 34 & {\rfour} & 31 & {\rfour}\\
camel1 & 34 & {\rthree} &$\bigstar$ 35 & {\rfour} & 31 &         & 33 & {\rtwo} & 33 & {\rtwo} & 30 &        \\
ivy0 & 27 &         & 30 & {\rone} & 30 & {\rone} & 32 & {\rthree} &$\bigstar$ 35 & {\rfour} &$\bigstar$ 35 & {\rfour}\\
jedit0 & 50 &         & 55 & {\rtwo} & 56 & {\rtwo} & 55 & {\rtwo} &$\bigstar$ 61 & {\rfour} & 60 & {\rfour}\\
jedit1 & 37 & {\rone} & 34 &         & 36 &         & 47 & {\rfour} & 45 & {\rthree} &$\bigstar$ 48 & {\rfour}\\
jedit2 & 4 &         &$\bigstar$ 99 & {\rfour} & 5 &         & 9 &         & 9 &         & 11 &        \\
log4j0 & 62 & {\rfour} & 7 &         & 47 & {\rthree} &$\bigstar$ 64 & {\rfour} & 53 & {\rfour} & 45 & {\rthree}\\
lucene0 & 70 & {\rthree} & 73 & {\rfour} & 56 &         &$\bigstar$ 75 & {\rfour} & 70 & {\rthree} &$\bigstar$ 75 & {\rfour}\\
poi0 &$\bigstar$ 78 & {\rfour} & 63 &         & 74 & {\rthree} & 70 & {\rtwo} & 73 & {\rthree} & 72 & {\rtwo}\\
poi1 & 5 &         &$\bigstar$ 78 & {\rfour} & 21 & {\rone} &$\bigstar$ 78 & {\rfour} & 76 & {\rfour} &$\bigstar$ 78 & {\rfour}\\
synapse0 & 0 &         & 2 &         & 40 & {\rthree} &$\bigstar$ 56 & {\rfour} & 52 & {\rfour} & 55 & {\rfour}\\
velocity0 & 51 &         & 51 &         & 49 &         & 51 &         & 53 & {\rone} &$\bigstar$ 59 & {\rfour}\\
xerces0 & 22 & {\rthree} & 20 & {\rone} & 21 & {\rtwo} & 18 &         & 23 & {\rfour} & 22 & {\rthree}\\
xerces1 & 23 & {\rone} & 2 &         & 18 & {\rone} & 36 & {\rtwo} & 68 & {\rfour} &$\bigstar$ 71 & {\rfour}\\
\end{tabular}
\end{minipage}\begin{minipage}{.15\linewidth}
\begin{tabular}{|p{\linewidth}|}\hline

@@

\begin{figure}[!t]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
Some goals related to aspects of defect prediction:
\be
\item
Mission-critical systems are risk averse and may accept very high false alarm rates,
just as long as they catch any life-threatening possibility. That is, such projects
do not care about effort- they want to {\em maximize recall} regardless of any impact
that might have on the false alarm rate.
\item
Cost averse managers may accept lower probabilities of
detection (the recall measure), just as long as they {\em do not waste budgets on false alarms}. This community
seeks to {\em minimize false alarms} while maintaining {\em some level of adequate recall}.
\item  Suppose a new hire wants
 to impress their manager. That 
 new hire might want to ensure that no result presented to  management contains  true negative;
i.e. they wish to {\em maximize precision}.
\item
Some communities do not care about   low precision,
just as long as a small fraction the data is returned. Hayes, Dekhytar, \& Sundaram call this fraction 
{\em selectivity} and offer an
extensive discussion of the merits of this measure~\cite{hayes06}.
\ee
\\\hline
Beyond defect prediction are other goals that combine defect prediction with other economic
factors:
\be
\setcounter{enumi}{4}
\item
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.
\item In other work, Yin et al. are concerned about
 {\em incorrect bug fixes}; i.e. those that require subsequent work in order to complete the bug fix.
These bugs occur  when (say) developers try to fix parts of the code
where they have very little experience~\cite{yin11}.  To avoid such incorrect bug fixes, we have to optimize
for finding the most number of bugs in regions that {\em the most programmers have worked with before}.
\item In {\em Better-faster-cheaper}, we seek  project changes that lead
to fewer defects and faster development times using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.
\item {\em  Rush-to-market} is another economic-based optimization measure.
A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
used to subsequently fix any issues with version 1.0)~\cite{huang06}.
\ee
\\\hline
All the above measures relate to the tendency of a predictor to find something. Another style
of measure would be to check the {\em variability} of that predictor:
\be
\setcounter{enumi}{8}
\item
In their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.
\ee
\\\hline
\end{tabular}
\caption{Reasoning about software many have many different goals including the nine shown here. Many of
these goals are defined in terms of 
\fig{criteria}.
}\label{fig:goals}
\end{figure}
\fig{goals} lists other performance measures that we have seen at client sites or in the literature. Note that:
\be
\item This list is very long.
\item This list keeps growing.
\ee As to this second point,
often when we work
with new clients, they surprise us with yet another domain-specific criteria that is important for the business.
That is, neither \fig{criteria} or \fig{goals} is not a complete list of all possible assessment criteria.

Our reading of the defect prediction literature is that most papers only explore a small subset of 
 \fig{criteria} or \fig{goals}. We think this is a mistake and researchers should more to a more general
framework where they explore a wide and changing set of evaluation criteria. 
Hence, this paper.
